Dish: Distribution-oblivious Shell Scripting

### 2019-11-22 pldi/draft.tex
Limitations

\paragraph{Assumptions}

\kk{This paragraph is not extremely necessary. Maybe it can be moved
  to limitations?}

There are two additional assumptions that have to be satisfied in
order for the distributed implementation that is generated by Dish to
have equivalent behaviour with the original implementation. First of
all, there should be no external signals to the commands while they
execute. At the moment Dish assumes no faults, and that communication
always succeeds. This assumption can be lifted by extending Dish with
a fault-tolerant runtime, \kk{blah blah}. Second, we assume that no
command reads and writes to arbitrary files that are not mentioned in
their arguments. This is a necessary assumption, since commands are
considered as black boxes and the only information that can be
inferred about them is through their arguments.

@@

\section{Limitations}

\kk{This is not really a section on its own, but rather part of something else.}

\begin{itemize}
\item Fault Tolerance
\item Distributed Planning: The planner at the moment is naive, and
  there is a huge literature on operator placement of distributed
  dataflow graphs that can be used to improve it.
\item Support of shell constructs: At the moment we have been
  conservative in the shell subsets that we handle, so that we don't
  introduce any unsafe parallelism. The point of this work was not to
  be able to handle a complete distributable subset of the shell, but
  rather a significantly big part of it, to demonstrate that there can
  be performance benefit from it.
\item Support distributing different classes: At the moment we are
  only dealing with stateless and pure commands, that is the ones that
  are most popular but also can offer the biggest benefits from
  parallelizing them. However, it would be interesting to explore the
  distributability of the file system commands, by using a distributed
  file system. THis would also require considerations about
  replication, consistency, and failures.
\item No cycles (multiple commands writing and reading from the same file)
\item Formal proof that the analysis indeed returns distributable
  subtrees. Previously there was no formal semantics for shell, but
  recent work (cite greenberg) allows us to make a formal proof that
  the analysis is indeed sound.
\end{itemize}

@@

\kk{We need to cite DGSH}

\section{Conclusion}
\label{discussion}

>>>>

@@

@@

\heading{Concurrent and Distributed Shells}
Among other work, the Smoosh authors have argued that certain features of the shell are useful for concurrency~\cite{smoosh:18}.
However, their work is 
dgsh~\cite{dagsh:17}.

\section{Discussion}
\label{discussion}

This section reflects on \sys's design and implementation, touches on future work, and closes the paper.

\heading{Limitations}
Our is implementation is limited in many ways, so as to succeed in proving the key hypothesis---that scaling out shell pipelines can be automated and correct--- despite \sys being a research prototype.

\sys does not adequately handle failures or network partitions in the general sense, which would include re-scheduling passes that were executing on failed replicas.
Prior work on fault-tolerant distributed stream processing~\cite{} can be of significant aid here.

The logic of the planner is quite simplified, attempting only straightforward placement of tasks to nodes (and using a hard-coded, homogeneous node structure).
Prior work on operator placement of distributed dataflow graphs~\cite{} can be used to improve it.

\sys is conservative in the shell subsets that it handles, so that it doesn't introduce any unsafe parallelism.
The point of this work was not to be able to handle a complete distributable
subset of the shell, but rather use significant part of it to demonstrate
performance benefits.

\heading{Future Work}
% \label{limitation}
% \item No cycles (multiple commands writing and reading from the same file)
There are several worthwhile directions for future work.
One direction would be a formal study of \sys and specifically a proof that the analysis~\sx{dataflow} does indeed return distributable subtrees.
Recent work on formalizing the semantics of the POSIX shell~\cite{smoosh:20} make such an attempt possible.

Another direction is to extend \sys to handle other classes outside \sta and \pur.
These two classes enjoy a certain in quick, one-off pipelines and are the easiest to distribute, but 
it would be interesting to expand to \dfs (with the use of a distributed file-system) and \sid (with the use of transactional protocols).
This direction would naturally introduce considerations about replication, consistency, and failure recovery.

% There are two additional assumptions that have to be satisfied in
% order for the distributed implementation that is generated by Dish to
% have equivalent behaviour with the original implementation. First of
% all, there should be no external signals to the commands while they
% execute. At the moment Dish assumes no faults, and that communication
% always succeeds. This assumption can be lifted by extending Dish with
% a fault-tolerant runtime, \kk{blah blah}. Second, we assume that no
% command reads and writes to arbitrary files that are not mentioned in
% their arguments. This is a necessary assumption, since commands are
% considered as black boxes and the only information that can be
% inferred about them is through their arguments.

\heading{Conclusion}
This paper presented \sys, a shell variant that automatically and correctly scales out distribution-oblivious shell pipelines. 
\sys's insight is that shell pipelines already express stream computations that can be automatically distributed.
To achieve this, \sys
  decomposes primitives into distributability classes,
  identifies high-distributability stages,
  applies rewriting rules for largest possible subprograms,
  and orchestrates the execution of the distributed program.
% Its runtime component provides orchestration and planning support during the execution of the program.
Experiments with complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.
